D3064R0: OOTA Execution is Provably Vacuous

### 2023-12-03 ootavacuous.tex
Add script to auto-format/include litmus tests
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

\begin{listing}[tbp]
\begin{verbatim}
 1 C oota-causality-5
 2 {
 3   [x] = 0;
 4   [y] = 0;
 5   [z] = 0;
 6 }
 7
 8 P0(atomic_int *x, atomic_int *y, atomic_int *z) {
 9   int r1 = atomic_load_explicit(x, memory_order_relaxed);
10   atomic_store_explicit(y, r1, memory_order_relaxed);
11 }
12
13 P1(atomic_int *x, atomic_int *y, atomic_int *z) {
14   int r2 = atomic_load_explicit(y, memory_order_relaxed);
15   atomic_store_explicit(x, r2, memory_order_relaxed);
16 }
17
18 P2(atomic_int *x, atomic_int *y, atomic_int *z) {
19   atomic_store_explicit(z, 1, memory_order_relaxed);
20 }
21
22 P3(atomic_int *x, atomic_int *y, atomic_int *z) {
23   int r3 = atomic_load_explicit(z, memory_order_relaxed);
24   atomic_store_explicit(x, r3, memory_order_relaxed);
25 }
26
27 exists(0:r1=1 /\ 1:r2=1 /\ 3:r3=0)
\end{verbatim}
\caption{Causality Test Case 5}
\label{lst:Causality Test Case 5}
\end{listing}

@@

\begin{listing}[tbp]
\begin{verbatim}
 1 C oota-non-lb
 2 {
 3   [x] = 2;
 4   [y] = 1;
 5   [z] = 1;
 6 }
 7
 8 P0(atomic_int *x, atomic_int *y, atomic_int *z) {
 9   int r0 = atomic_load_explicit(y, memory_order_relaxed);
10   int r1 = atomic_load_explicit(z, memory_order_relaxed);
11   int r2 = r0 + r1;
12   atomic_store_explicit(x, r2, memory_order_relaxed);
13 }
14
15 P1(atomic_int *x, atomic_int *y, atomic_int *z) {
16   int r3 = atomic_load_explicit(x, memory_order_relaxed);
17   atomic_store_explicit(y, r3 / 2, memory_order_relaxed);
18 }
19
20 P2(atomic_int *x, atomic_int *y, atomic_int *z) {
21   int r4 = atomic_load_explicit(x, memory_order_relaxed);
22   atomic_store_explicit(z, r4 / 2, memory_order_relaxed);
23 }
24
25 locations [0:r0;0:r1;0:r2;1:r3;2:r4]
26 exists(x=42 /\ y=21 /\ z=21)
\end{verbatim}
\caption{Non-LB Litmus Test}
\label{lst:Non-LB Litmus Test}
\end{listing}

>>>>

\begin{listing}[tbp]
\begin{verbatim}
@@ DisplayLitmus litmus/oota-causality-5.litmus @@
\end{verbatim}
\caption{Causality Test Case 5}
\label{lst:Causality Test Case 5}
\end{listing}

@@

\begin{listing}[tbp]
\begin{verbatim}
@@ DisplayLitmus litmus/oota-non-lb.litmus @@
\end{verbatim}
\caption{Non-LB Litmus Test}
\label{lst:Non-LB Litmus Test}
\end{listing}

\subsubsection{Multi-Cycle Litmus Tests}
\label{app:Multi-Cycle Litmus Tests}

\begin{listing}[tbp]
\begin{verbatim}
@@ DisplayLitmus litmus/oota-two-source.litmus @@
\end{verbatim}
\caption{Multi-Cycle Litmus Test}
\label{lst:Multi-Cycle Litmus Test}
\end{listing}
